\documentclass{article}
\usepackage{amsmath, amssymb}

\begin{document}

\section*{1.1}
Let $V$ be a pre-Hilbert space. Use $0 \leq \langle \alpha x + \beta y, \alpha x + \beta y \rangle$ for $\alpha, \beta \in \mathbb{R}$ and $x, y \in V$ to prove the Cauchy–Schwarz inequality.
\\
\\
\noindent \textbf{SOLUTION: }\\

\noindent Let $x, y \in \mathbb{V}, \alpha, \beta \in \mathbb{R}$, $0 \leq \langle \alpha x + \beta y ,\alpha x + \beta y  \rangle$. Without loss of generality 
take $\beta = 1$. Then, by the linearity of $\langle \star, \cdot \rangle$ follows:

\begin{align*}
    0 &\leq \langle \alpha x + y, \alpha x + y,\rangle \\
    &= \langle \alpha x, \alpha x \rangle + \langle \alpha x, y \rangle + \langle y, \alpha x \rangle + \langle y, y \rangle \\
    &= \alpha^2 \langle x, x \rangle + \alpha \langle x, y \rangle + \alpha \langle y, x \rangle + \langle y, y \rangle \\
    &= \alpha^2 \| x \|^2 + 2 \alpha \langle x, y \rangle + \| y \|^2
\end{align*}

\noindent The minimum (as a function of $\alpha$) is attained when:
\[ 
    \alpha^2 \| x \|^2 + 2 \alpha \langle x, y \rangle + \| y \|^2 = 0
\] Note that because this polynomial as a function of $\alpha$ is a quadratic polynomial, it has at most one real root. Therefore 
the discriminant must be non-positive, i.e. $4\langle x, y \rangle^2 - 4 \| x \|^2 \| y \|^2 \leq 0$, which is equivalent to
the Cauchy-Schwarz-Bunyakowsky inequality.

\section*{1.2}
Let $V$ be a normed space with norm $\| \cdot \| : V \to \mathbb{R}$. Show that $V$ is a pre-Hilbert space and that the norm comes from an inner product $\langle \cdot, \cdot \rangle : V \times V \to \mathbb{R}$ if and only if the parallelogram equality
\[
\|x + y\|^2 + \|x - y\|^2 = 2\|x\|^2 + 2\|y\|^2, \quad x, y \in V
\]
holds, and that in this case the inner product satisfies
\[
\langle x, y \rangle = \frac{1}{4} \left( \|x + y\|^2 - \|x - y\|^2 \right), \quad x, y \in V.
\]

\noindent \textbf{SOLUTION: }\\
$\leftleftarrows]$

\section*{1.3}
Let $V$ be a pre-Hilbert space. Show that the norm induced by the inner product satisfies $\|x + y\| < 2$ for all $x \neq y \in V$ with $\|x\| = \|y\| = 1$.
\\
\\
\noindent \textbf{SOLUTION: }
We know that $\langle \star, \star \rangle^{\frac{1}{2}} =  \| \star \|$. By ex. $1.2$ this implies the internal product can be expressed in 
\section*{1.4}
Let $A \in \mathbb{R}^{n \times n}$ be symmetric and positive definite and let $C \in \mathbb{R}^{n \times m}$. Show:
\begin{enumerate}
    \item the matrix $C^\top AC$ is positive semi-definite,
    \item $\text{rank}(C^\top AC) = \text{rank}(C)$,
    \item the matrix $C^\top AC$ is positive definite if and only if $\text{rank}(C) = m$.
\end{enumerate}

\section*{1.5}
Show that a matrix $A \in \mathbb{R}^{n \times n}$ is symmetric and positive definite if and only if it is of the form $A = B B^\top$ with an invertible matrix $B \in \mathbb{R}^{n \times n}$.

\section*{1.6}
Let $A, B, C \in \mathbb{R}^{2 \times 2}$ with $C = AB$. Let
\[
p = (a_{11} + a_{22})(b_{11} + b_{22}), \quad q = (a_{21} + a_{22})b_{11},
\]
\[
r = a_{11}(b_{12} - b_{22}), \quad s = a_{22}(b_{21} - b_{11}),
\]
\[
t = (a_{11} + a_{12})b_{22}, \quad u = (a_{21} - a_{11})(b_{11} + b_{12}),
\]
\[
v = (a_{12} - a_{22})(b_{21} + b_{22}).
\]
Show that the elements of $C$ can then be computed via
\[
c_{11} = p + s - t + v, \quad c_{12} = r + t,
\]
\[
c_{21} = q + s, \quad c_{22} = p + r - q + u.
\]
Compare the number of multiplications and additions for this method with the number of multiplications and additions for the standard method of multiplying two $2 \times 2$ matrices.

Finally, show that if the above method is recursively applied to matrices $A, B \in \mathbb{R}^{n \times n}$ with $n = 2^k$, then the method requires $7^k$ multiplications and $6 \cdot 7^k - 6 \cdot 2^{2k}$ additions and subtractions.

\end{document}
